Challenges in Developing Great Quasi-Monte Carlo Software

### 2023-10-19 HickernellToTheMCQMC2022EditorsVersion2/MCQMC2022ChallengesQMCSoftwareArticle_revision_2_toeditors.tex
Fred 2023 Mac M2 Updates

%%%%Fred start
\input{common-macros.tex}
\usepackage{cite}
\usepackage{xspace}
\usepackage[bookmarks=false]{hyperref}
\usepackage[hyphens]{url}
\providecommand{\HickernellFJ}{Hickernell\xspace}
\graphicspath{{ProgramsImages/}}

@@

\bibliographystyle{spmpsci}
\bibliography{FJH23,FJHown23,sc}

>>>>

%%%%Fred start
\input{common-macros.tex}
\usepackage{cite}
\usepackage{xspace}
\usepackage[bookmarks=false]{hyperref}
\usepackage[hyphens]{url}
%\providecommand{\HickernellFJ}{Hickernell\xspace}
%\graphicspath{{ProgramsImages/}}

@@

%\bibliographystyle{spmpsci}
%\bibliography{FJH23,FJHown23,sc}

%\def\Ignore#1{}\def\notesupp#1{}\providecommand{\HickernellFJ}{Hickernell\xspace}\def\Ignore#1{}\def\notesupp#1{}\providecommand{\HickernellFJ}{Hickernell\xspace}
\begin{thebibliography}{10}
	\providecommand{\url}[1]{{#1}}
	\providecommand{\urlprefix}{URL }
	\expandafter\ifx\csname urlstyle\endcsname\relax
	\providecommand{\doi}[1]{DOI~\discretionary{}{}{}#1}\else
	\providecommand{\doi}{DOI~\discretionary{}{}{}\begingroup
		\urlstyle{rm}\Url}\fi

	\bibitem{QMCJulia}
	{SciML QuasiMonteCarlo.jl} (2022).
	\newblock \urlprefix\url{https://github.com/SciML/QuasiMonteCarlo.jl}

	\bibitem{DakotaUsersManual}
	Adams, B.M., Bohnhoff, W.J., Dalbey, K.R., Ebeida, M.S., Eddy, J.P., Eldred,
	M.S., Hooper, R.W., Hough, P.D., Hu, K.T., Jakeman, J.D., Khalil, M., Maupin,
	K.A., Monschke, J.A., Ridgway, E.M., Rushdi, A.A., Seidl, D.T., Stephens,
	J.A., Swiler, L.P., Tran, A., Winokur, J.G.: Dakota, A Multilevel Parallel
	Object-Oriented Framework for Design Optimization, Parameter Estimation,
	Uncertainty Quantification, and Sensitivity Analysis: Version 6.16 User's
	Manual.
	\newblock Sandia National Laboratories (2022)

	\bibitem{osti_1846008}
	Bernholdt, D.E., Cary, J., Heroux, M., McInnes, L.C.: The science of
	scientific-software development and use  (2022).
	\newblock \doi{10.2172/1846008}.
	\newblock \urlprefix\url{https://www.osti.gov/biblio/1846008}

	\bibitem{BraFox88}
	Bratley, P., Fox, B.L.: Algorithm 659: Implementing {Sobol's} quasirandom
	sequence generator.
	\newblock ACM Trans.\ Math.\ Software \textbf{14}, 88--100 (1988)

	\bibitem{BraFoxNie92}
	Bratley, P., Fox, B.L., Niederreiter, H.: Implementation and tests of
	low-discrepancy sequences.
	\newblock ACM Trans.\ Model.\ Comput.\ Simul. \textbf{2}, 195--213 (1992)

	\bibitem{MCQMC2022Figs}
	Choi, S.C.T., Ding, Y., Hickernell, F.J., Jagadeeswaran, R., Sorokin, A.G.:
	{MCQMC} 2022 figures.
	\newblock
	\urlprefix\url{https://github.com/QMCSoftware/QMCSoftware/tree/develop/demos/talk_paper_demos/MCQMC2022_Article_Figures}

	\bibitem{QMCPy2020a}
	Choi, S.C.T., Hickernell, F.J., Jagadeeswaran, R., McCourt, M., Sorokin, A.:
	{QMCPy}: A quasi-{M}onte {C}arlo {P}ython library (versions 1--1.4) (2023).
	\newblock \doi{10.5281/zenodo.3964489}.
	\newblock \urlprefix\url{https://qmcsoftware.github.io/QMCSoftware/}

	\bibitem{ChoEtal22a}
	Choi, S.C.T., Hickernell, F.J., Jagadeeswaran, R., McCourt, M.J., Sorokin,
	A.G.: Quasi-{M}onte {C}arlo software.
	\newblock In: A.~Keller (ed.) {M}onte {C}arlo and Quasi-{M}onte {C}arlo
	Methods: {MCQMC}, {O}xford, England, {A}ugust 2020, Springer Proceedings in
	Mathematics and Statistics, pp. 23--50. Springer, Cham (2022).
	\newblock \url{https://arxiv.org/abs/2102.07833}

	\bibitem{DicEtal22a}
	Dick, J., Kritzer, P., Pillichshammer, F.: Lattice Rules: {N}umerical
	Integration, Approximation, and Discrepancy.
	\newblock Springer Series in Computational Mathematics. Springer Cham (2022).
	\newblock \doi{https://doi.org/10.1007/978-3-031-09951-9}

	\bibitem{DicEtal14a}
	Dick, J., Kuo, F., Sloan, I.H.: High dimensional integration --- the
	{Q}uasi-{M}onte {C}arlo way.
	\newblock Acta Numer. \textbf{22}, 133--288 (2013).
	\newblock \doi{10.1017/S0962492913000044}

	\bibitem{K23}
	Finley, K.: Non-code contributions are the secret to open source success.
	\newblock The ReadME Project, GitHub (2023).
	\newblock
	\urlprefix\url{https://github.com/readme/featured/open-source-non-code-contributions}

	\bibitem{FriKelweb}
	Friedel, I., Keller, A.: libseq -- low discrepancy sequence library (2001).
	\newblock \urlprefix\url{http://www.multires.caltech.edu/software/libseq/}

	\bibitem{FriKel02}
	Friedel, I., Keller, A.: Fast generation of randomized low-discrepancy point
	sets.
	\newblock In: K.T. Fang, F.J. Hickernell, H.~Niederreiter (eds.) {M}onte
	{C}arlo and Quasi-{M}onte {C}arlo Methods 2000, pp. 257--273.
	Springer-Verlag, Berlin (2002)

	\bibitem{GelEtal13}
	Gelman, A., Carlin, J.B., Stern, H.S., Dunson, D.B., Vehtari, A., Rubin, D.B.:
	Bayesian Data Analysis.
	\newblock CRC Texts in Statistical Science. Chapman \& Hall (2013)

	\bibitem{Gla03}
	Glasserman, P.: {M}onte {C}arlo Methods in Financial Engineering,
	\emph{Applications of Mathematics}, vol.~53.
	\newblock Springer-Verlag, New York (2004)

	\bibitem{GruWeb}
	Gr\"unschlo{\ss}, L.: Leonhard gr\"unschlo{\ss}'s webpage.
	\newblock \urlprefix\url{https://gruenschloss.org}

	\bibitem{HicEtal18a}
	Hickernell, F.J., Choi, S.C.T., Jiang, L., {Jim\'enez Rugama}, {\relax
		Ll}.A.: {M}onte {C}arlo simulation, automatic stopping criteria for.
	\newblock In: M.~Davidian, B.~Everitt, R.S. Kenett, G.~Molenberghs,
	W.~Piegorsch, F.~Ruggeri (eds.) Wiley StatsRef-Statistics Reference Online.
	John Wiley \& Sons Ltd. (2018).
	\newblock \doi{10.1002/9781118445112.stat08035}

	\bibitem{HicEtal14a}
	Hickernell, F.J., Jiang, L., Liu, Y., Owen, A.B.: Guaranteed conservative
	fixed width confidence intervals via {M}onte {C}arlo sampling.
	\newblock In: J.~Dick, F.Y. Kuo, G.W. Peters, I.H. Sloan (eds.) {M}onte {C}arlo
	and Quasi-{M}onte {C}arlo Methods 2012, \emph{Springer Proceedings in
		Mathematics and Statistics}, vol.~65, pp. 105--128. Springer-Verlag, Berlin
	(2013).
	\newblock \doi{10.1007/978-3-642-41095-6}

	\bibitem{HicJim16a}
	Hickernell, F.J., {Jim\'enez Rugama}, {\relax Ll}.A.: Reliable adaptive
	cubature using digital sequences.
	\newblock In: R.~Cools, D.~Nuyens (eds.) {M}onte {C}arlo and Quasi-{M}onte
	{C}arlo Methods: {MCQMC}, {L}euven, {B}elgium, {A}pril 2014, \emph{Springer
		Proceedings in Mathematics and Statistics}, vol. 163, pp. 367--383.
	Springer-Verlag, Berlin (2016).
	\newblock ArXiv:1410.8615 [math.NA]

	\bibitem{HicEtal17a}
	Hickernell, F.J., {Jim\'enez Rugama}, {\relax Ll}.A., Li, D.: Adaptive
	quasi-{M}onte {C}arlo methods for cubature.
	\newblock In: J.~Dick, F.Y. Kuo, H.~Wo\'zniakowski (eds.) Contemporary
	Computational Mathematics --- a celebration of the 80th birthday of {I}an
	{S}loan, pp. 597--619. Springer-Verlag (2018).
	\newblock \doi{10.1007/978-3-319-72456-0}

	\bibitem{QRNG2020}
	Hofert, M., Lemieux, C.: qrng {R} package (2017).
	\newblock \urlprefix\url{https://cran.r-project.org/web/packages/qrng/qrng.pdf}

	\bibitem{HonHic00a}
	Hong, H.S., Hickernell, F.J.: Algorithm 823: Implementing scrambled digital
	nets.
	\newblock ACM Trans.\ Math.\ Software \textbf{29}, 95--109 (2003).
	\newblock \doi{10.1145/779359.779360}

	\bibitem{RatHic19a}
	Jagadeeswaran, R., Hickernell, F.J.: Fast automatic {B}ayesian cubature
	using lattice sampling.
	\newblock Stat.\ Comput. \textbf{29}, 1215--1229 (2019).
	\newblock \doi{10.1007/s11222-019-09895-9}

	\bibitem{JagHic22a}
	Jagadeeswaran, R., Hickernell, F.J.: Fast automatic {B}ayesian cubature
	using {S}obol' sampling.
	\newblock In: Z.~Botev, A.~Keller, C.~Lemieux, B.~Tuffin (eds.) Advances in
	Modeling and Simulation: {F}estschrift in Honour of {P}ierre {L'E}cuyer, pp.
	301--318. Springer, Cham (2022).
	\newblock \doi{10.1007/978-3-031-10193-9\_15}

	\bibitem{Jia16a}
	Jiang, L.: Guaranteed adaptive {M}onte {C}arlo methods for estimating means of
	random variables.
	\newblock Ph.D. thesis, Illinois Institute of Technology (2016)

	\bibitem{GilJim16b}
	{Jim\'enez Rugama}, {\relax Ll}.A., Gilquin, L.: Reliable error estimation for
	{S}obol' indices.
	\newblock Statistics and Computing \textbf{28}, 725--738 (2018).
	\newblock \doi{10.1007/s11222-017-9759-1}

	\bibitem{JimHic16a}
	{Jim\'enez Rugama}, {\relax Ll}.A., Hickernell, F.J.: Adaptive
	multidimensional integration based on rank-1 lattices.
	\newblock In: R.~Cools, D.~Nuyens (eds.) {M}onte {C}arlo and Quasi-{M}onte
	{C}arlo Methods: {MCQMC}, {L}euven, {B}elgium, {A}pril 2014, \emph{Springer
		Proceedings in Mathematics and Statistics}, vol. 163, pp. 407--422.
	Springer-Verlag, Berlin (2016).
	\newblock ArXiv:1411.1966

	\bibitem{SobolDirection}
	Joe, S., Kuo, F.Y.: Sobol sequence generator.
	\newblock \urlprefix\url{https://web.maths.unsw.edu.au/~fkuo/sobol/}

	\bibitem{JoeKuo03}
	Joe, S., Kuo, F.Y.: Remark on algorithm 659: Implementing {S}obol's quasirandom
	sequence generator.
	\newblock ACM Trans.\ Math.\ Software \textbf{29}, 49--57 (2003)

	\bibitem{KuoJoe08a}
	Joe, S., Kuo, F.Y.: Constructing {S}obol sequences with better two-dimensional
	projections.
	\newblock SIAM J.\ Sci.\ Comput. \textbf{30}, 2635--2654 (2008)

	\bibitem{Kmmerer2015}
	K\"{a}mmerer, L., Potts, D., Volkmer, T.: Approximation of multivariate
	periodic functions by trigonometric polynomials based on rank-1 lattice
	sampling.
	\newblock J.\ Complexity \textbf{31}(4), 543--576 (2015).
	\newblock \doi{10.1016/j.jco.2015.02.004}.
	\newblock \urlprefix\url{https://doi.org/10.1016/j.jco.2015.02.004}

	\bibitem{SamplePack}
	Kollig, T., Keller, A.: Samplepack (2002).
	\newblock \urlprefix\url{https://www.uni-kl.de/AG-Heinrich/SamplePack.html}

	\bibitem{BRODA20a}
	Kucherenko, S.: {BRODA} (2022).
	\newblock \urlprefix\url{https://www.broda.co.uk/index.html}

	\bibitem{KuoNuy16a}
	Kuo, F.Y., Nuyens, D.: Application of quasi-{M}onte {C}arlo methods to elliptic
	{PDE}s with random diffusion coefficients -- a survey of analysis and
	implementation.
	\newblock Found.\ Comput.\ Math. \textbf{16}, 1631--1696 (2016).
	\newblock \urlprefix\url{https://people.cs.kuleuven.be/~dirk.nuyens/qmc4pde/}

	\bibitem{LEcEtal22a}
	L'Ecuyer, P., Marion, P., Godin, M., Puchhammer, F.: A tool for custom
	construction of {QMC} and {RQMC} point sets.
	\newblock In: A.~Keller (ed.) {M}onte {C}arlo and Quasi-{M}onte {C}arlo
	Methods: {MCQMC}, {O}xford, 2020, Springer Proceedings in Mathematics and
	Statistics. Springer, Cham (2022)

	\bibitem{l2002ssj}
	L'Ecuyer, P., Meliani, L., Vaucher, J.: Ssj: A framework for stochastic
	simulation in {Java}.
	\newblock In: Proceedings of the Winter Simulation Conference, vol.~1, pp.
	234--242. IEEE (2002)

	\bibitem{l2018sorting}
	L'Ecuyer, P., Munger, D., L{\'e}cot, C., Tuffin, B.: Sorting methods and
	convergence rates for {Array-RQMC}: Some empirical comparisons.
	\newblock Mathematics and Computers in Simulation \textbf{143}, 191--201 (2018)

	\bibitem{LEcuyer2022b}
	L'Ecuyer, P., Puchhammer, F., {Ben Abdellah}, A.: Monte carlo and
	quasi{\textendash}monte carlo density estimation via conditioning.
	\newblock INFORMS J.\ Comput. \textbf{34}(3), 1729--1748 (2022).
	\newblock \doi{10.1287/ijoc.2021.1135}.
	\newblock \urlprefix\url{https://doi.org/10.1287/ijoc.2021.1135}

	\bibitem{Nie92}
	Niederreiter, H.: Random Number Generation and Quasi-{M}onte {C}arlo Methods.
	\newblock CBMS-NSF Regional Conference Series in Applied Mathematics. SIAM,
	Philadelphia (1992)

	\bibitem{NovWoz10a}
	Novak, E., Wo{\'{z}}niakowski, H.: Tractability of Multivariate Problems
	{V}olume {II}: {S}tandard Information for Functionals.
	\newblock No.~12 in EMS Tracts in Mathematics. European Mathematical Society,
	Z\"urich (2010)

	\bibitem{NuyWeb}
	Nuyens, D.: Dirk's homepage.
	\newblock \urlprefix\url{https://people.cs.kuleuven.be/~dirk.nuyens/}

	\bibitem{Owe22a}
	Owen, A.B.: On dropping the first {Sobol'} point.
	\newblock In: A.~Keller (ed.) {M}onte {C}arlo and Quasi-{M}onte {C}arlo
	Methods: {MCQMC}, {O}xford, England, {A}ugust 2020, Springer Proceedings in
	Mathematics and Statistics, pp. 71--86. Springer, Cham (2022).
	\newblock \urlprefix\url{https://arxiv.org/pdf/2008.08051.pdf}

	\bibitem{FinDer}
	Papageorgiou, A.: Finder.
	\newblock \urlprefix\url{http://www.cs.columbia.edu/~ap/html/finder.html}

	\bibitem{MUQ2}
	Parno, M., Davis, A., Seelinger, L.: {MUQ}: The {MIT} {U}ncertainty
	{Q}uantification library.
	\newblock Journal of Open Source Software \textbf{6}(68), 3076 (2021).
	\newblock \doi{10.21105/joss.03076}.
	\newblock \urlprefix\url{https://doi.org/10.21105/joss.03076}

	\bibitem{ParSee22a}
	Parno, M., Seelinger, L.: Uncertainty propagation of material properties of a
	cantilevered beam (2022).
	\newblock
	\urlprefix\url{https://um-bridge-benchmarks.readthedocs.io/en/docs/forward-benchmarks/muq-beam-propagation.html}

	\bibitem{PasTra95}
	Paskov, S., Traub, J.: Faster valuation of financial derivatives.
	\newblock J. Portfolio Management \textbf{22}, 113--120 (1995)

	\bibitem{paszke2019pytorch}
	Paszke, A., Gross, S., Massa, F., Lerer, A., Bradbury, J., Chanan, G., Killeen,
	T., Lin, Z., Gimelshein, N., Antiga, L., Desmaison, A., K{\"o}pf, A., Yang,
	E., DeVito, Z., Raison, M., Tejani, A., Chilamkurthy, S., Steiner, B., Fang,
	L., Bai, J., Chintala, S.: Py{T}orch: An imperative style, high-performance
	deep learning library.
	\newblock Advances in neural information processing systems \textbf{32},
	8026--8037 (2019)

	\bibitem{paulin2022}
	Paulin, L., Bonneel, N., Coeurjolly, D., Iehl, J.C., Keller, A., Ostromoukhov,
	V.: Matbuilder: Mastering sampling uniformity over projections.
	\newblock ACM Transactions on Graphics (Proceedings of SIGGRAPH) \textbf{41}(4)
	(2022).
	\newblock \doi{https://doi.org/10.1145/3528223.3530063}

	\bibitem{PotSch21}
	Potts, D., Schmischke, M.: Approximation of high-dimensional periodic functions
	with fourier-based methods.
	\newblock SIAM J.\ Numer.\ Anal. \textbf{59}(5), 2393--2429 (2021).
	\newblock \doi{10.1137/20M1354921}.
	\newblock \urlprefix\url{https://doi.org/10.1137/20M1354921}

	\bibitem{puchhammer2021variance}
	Puchhammer, F., Ben~Abdellah, A., L'Ecuyer, P.: Variance reduction with
	{Array-RQMC} for tau-leaping simulation of stochastic biological and chemical
	reaction networks.
	\newblock Bulletin of Mathematical Biology \textbf{83}(8), 91 (2021)

	\bibitem{pytorchSoboldiscussion2020a}
	{PyTorch Developers}: {S}obol point implementation (2020).
	\newblock \urlprefix\url{https://github.com/pytorch/pytorch/issues/32047}

	\bibitem{SAS_LD}
	{SAS Institute}: Sas documentation for the model procedure (2023).
	\newblock
	\urlprefix\url{https://documentation.sas.com/doc/en/pgmsascdc/9.4_3.4/etsug/etsug_model_sect197.htm}

	\bibitem{scipySobol2020a}
	{SciPy Developers}: {SciPy} discussion of {S}obol' sequence implementation
	(2020).
	\newblock \urlprefix\url{https://github.com/scipy/scipy/pull/10844}

	\bibitem{UMBridge23}
	Seelinger, L., Cheng-Seelinger, V., Davis, A., Parno, M., Reinarz, A.:
	{UM-Bridge}: {U}ncertainty quantification and modeling bridge.
	\newblock Journal of Open Source Software \textbf{8}(83), 4748 (2023).
	\newblock \doi{10.21105/joss.04748}.
	\newblock \urlprefix\url{https://doi.org/10.21105/joss.04748}

	\bibitem{seelinger2023lowering}
	Seelinger, L., Reinarz, A., Benezech, J., Lykkegaard, M.B., Tamellini, L.,
	Scheichl, R.: Lowering the entry bar to {HPC}-scale uncertainty
	quantification (2023)

	\bibitem{SloJoe94}
	Sloan, I.H., Joe, S.: Lattice Methods for Multiple Integration.
	\newblock Oxford University Press, Oxford (1994)

	\bibitem{smith2016software}
	Smith, A.M., Katz, D.S., Niemeyer, K.E.: Software citation principles.
	\newblock PeerJ Computer Science \textbf{2}, e86 (2016)

	\bibitem{JagSor23a}
	Sorokin, A.G., Jagadeeswaran, R.: Monte {C}arlo for vector functions of
	integrals.
	\newblock In: A.~Hinrichs, P.~Kritzer, F.~Pillichshammer (eds.) {M}onte {C}arlo
	and Quasi-{M}onte {C}arlo Methods: {MCQMC}, {L}inz, Austria, {J}uly 2022,
	Springer Proceedings in Mathematics and Statistics. Springer, Cham (2023+).
	\newblock Submitted for publication

	\bibitem{tfqfQMC2021a}
	{TF Quant Finance Contributors}: Quasi {M}onte-{C}arlo methods (2021).
	\newblock \urlprefix\url{https://github.com/google/tf-quant-finance/math/qmc}

	\bibitem{MAT9.13}
	{The MathWorks, Inc.}: {MATLAB} R2022b.
	\newblock Natick, MA (2022)

	\bibitem{NAG27}
	{The Numerical Algorithms Group}: The {NAG} Library.
	\newblock Oxford, {M}ark 27 edn. (2021)

	\bibitem{TonEtAl22a}
	Tong, X., Choi, S.C.T., Ding, Y., Hickernell, F.J., Jiang, L., {Jim\'enez
		Rugama}, {\relax Ll}.A., Jagadeeswaran, R., Zhang, K., Zhang, Y., Zhou, X.:
	Guaranteed automatic integration library {(GAIL)}: An open-source {MATLAB}
	library for function approximation, minimization, and integration.
	\newblock J. Open Res.\ Software \textbf{10}, 7 (2022).
	\newblock \doi{10.5334/jors.381}

	\bibitem{ASCR-SSSDU}
	{U.S. Department of Energy, Office of Advanced Scientific Computing Research}:
	Workshop on the science of scientific-software development and use (2021).
	\newblock
	\urlprefix\url{https://web.cvent.com/event/1b7d7c3a-e9b4-409d-ae2b-284779cfe72f/summary}

	\bibitem{virtanen2020scipy}
	Virtanen, P., Gommers, R., Oliphant, T.E., Haberland, M., Reddy, T.,
	Cournapeau, D., Burovski, E., Peterson, P., Weckesser, W., Bright, J.,
	van~der Walt, S.J., Brett, M., Wilson, J., Millman, K.J., Mayorov, N.,
	Nelson, A.R.J., Jones, E., Kern, R., Larson, E., Carey, C.J., Polat, I.,
	Feng, Y., Moore, E.W., VanderPlas, J., Laxalde, D., Perktold, J., Cimrman,
	R., Henriksen, I., Quintero, E.A., Harris, C.R., Archibald, A.M., Ribeiro,
	A.H., Pedregosa, F., van Mulbregt, P., Vijaykumar, A., Bardelli, A.P.,
	Rothberg, A., Hilboll, A., Kloeckner, A., Scopatz, A., Lee, A., Rokem, A.,
	Woods, C.N., Fulton, C., Masson, C., H{\"a}ggstr{\"o}m, C., Fitzgerald, C.,
	Nicholson, D.A., Hagen, D.R., Pasechnik, D.V., Olivetti, E., Martin, E.,
	Wieser, E., Silva, F., Lenders, F., Wilhelm, F., Young, G., Price, G.A.,
	Ingold, G.L., Allen, G.E., Lee, G.R., Audren, H., Probst, I., Dietrich, J.P.,
	Silterra, J., Webber, J.T., Slavi{\v c}, J., Nothman, J., Buchner, J.,
	Kulick, J., Sch{\"o}nberger, J.L., de~Miranda~Cardoso, J., Reimer, J.,
	Harrington, J., Rodr{\'\i}guez, J.L.C., Nunez-Iglesias, J., Kuczynski, J.,
	Tritz, K., Thoma, M., Newville, M., K{\"u}mmerer, M., Bolingbroke, M.,
	Tartre, M., Pak, M., Smith, N.J., Nowaczyk, N., Shebanov, N., Pavlyk, O.,
	Brodtkorb, P.A., Lee, P., McGibbon, R.T., Feldbauer, R., Lewis, S., Tygier,
	S., Sievert, S., Vigna, S., Peterson, S., More, S., Pudlik, T., Oshima, T.,
	Pingel, T.J., Robitaille, T.P., Spura, T., Jones, T.R., Cera, T., Leslie, T.,
	Zito, T., Krauss, T., Upadhyay, U., Halchenko, Y.O., V{\'a}zquez-Baeza, Y.,
	Contributors: Scipy 1.0: fundamental algorithms for scientific computing in
	python.
	\newblock Nature Methods \textbf{17}(3), 261--272 (2020)

	\bibitem{Woz99a}
	Wo{\'z}niakowski, H.: Efficiency of quasi-{M}onte {C}arlo algorithms for high
	dimensions.
	\newblock In: H.~Niederreiter, J.~Spanier (eds.) {M}onte {C}arlo and
	Quasi-{M}onte {C}arlo Methods 1998, pp. 114--136. Springer-Verlag, Berlin
	(2000)

\end{thebibliography}
